Robust Clustering for Ad Hoc Cognitive Radio Network

### 2017-08-13 journal-draft/ettdoc_baseline.tex
modified till the comment C1-6

\title{Robust Clustering for Ad Hoc Cognitive Radio Network}
%\author[1]{Di Li\thanks{li@umic.rwth-aachen.de}}
%\author[2]{Erwin Fang\thanks{xx}}
%\author[3]{James Gross}
\author{Di Li\textsuperscript{1}, Erwin Fang\textsuperscript{2}, James Gross\textsuperscript{3}\corrauth}
%\affil[1]{RWTH Aachen University}
%\affil[2]{ETH Zurich}
%\affil[3]{KTH Royal Institute of Technology}
\address{RWTH Aachen University\textsuperscript{1}, Swisscom (Schweiz) AG\textsuperscript{2}, KTH Royal Institute of Technology\textsuperscript{3} }
%\renewcommand\Authands{ and }
\corraddr{Communication Theory Lab
School of Electrical Engineering, 
KTH Royal Institute of Technology
SE - 100 44 Stockholm\\Email: james.gross@ee.kth.se}

@@

\section{Performance Evaluation}
\label{performance}
%In this section, we evaluate the performances of ROSS.
The schemes involved in the simulation are as follows,
\begin{itemize}
\item ROSS without size control, \ie ROSS-DGA, ROSS-DFA.
\item ROSS with size control, \ie ROSS-$\delta$-DGA and ROSS-$\delta$-DFA where $\delta$ is the desired cluster size.
In the following, we refer to the above mentioned four schemes as the variants of ROSS.
\item SOC~\cite{LIU_TMC11_2}, a distributed clustering scheme pursuing cluster robustness.
\item Centralized robust clustering scheme. 
As shown in Section~\ref{centralized_solution}, the centralized robust clustering scheme is formulated as an integer linear optimization problem and is solved by MATLAB with the function $bintprog$.
\end{itemize}

@@

%This means that the sizes of the clusters generated by ROSS-DGA are limited by the network density, and the size control feature further restricts the appearances of the big clusters, thus when the variants of ROSS are implemented, most of the CR nodes are in the clusters which are slightly smaller than the desired size.

@@

The limitation of distributed scheme ROSS is it doesn't generate clusters whose sizes exceed the cluster head's neighborhood.
The reason is with ROSS, cluster heads form clusters on the basis of their neighborhood, and don't involve the nodes which are outside the neighborhood.
%In the other way around, forming big cluster which extends a cluster head's neighborhood has limited application scenarios, as multiple hop communication and coordination are required within these clusters.

>>>>

\title{Robust Clustering for Ad Hoc Cognitive Radio Network}
%\author[1]{Di Li\thanks{li@umic.rwth-aachen.de}}
%\author[2]{Erwin Fang\thanks{xx}}
%\author[3]{James Gross}
\author{Di Li\textsuperscript{1}\corrauth, Erwin Fang\textsuperscript{2}, James Gross\textsuperscript{3}}
%\affil[1]{RWTH Aachen University}
%\affil[2]{ETH Zurich}
%\affil[3]{KTH Royal Institute of Technology}
\address{RWTH Aachen University\textsuperscript{1}, Swisscom (Schweiz) AG\textsuperscript{2}, KTH Royal Institute of Technology\textsuperscript{3} }
%\renewcommand\Authands{ and }
%\corraddr{Communication Theory Lab
%School of Electrical Engineering, 
%KTH Royal Institute of Technology
%SE - 100 44 Stockholm\\Email: james.gross@ee.kth.se}
\corraddr{Chair of Communication and Distributed Systems
Ahornstraße 55 - building E3
52074 Aachen
Germany
\\Email: li@umic.rwth-aachen.de}

@@

\section{Performance Evaluation}
\label{performance}
%In this section, we evaluate the performances of ROSS.
The schemes involved in the simulation are as follows,
\begin{itemize}
\item ROSS without size control: ROSS-DGA, ROSS-DFA.
\item ROSS with size control, \ie ROSS-$\delta$-DGA and ROSS-$\delta$-DFA where $\delta$ is the desired cluster size.
In the following, we refer to the above mentioned four schemes as the variants of ROSS.
\item SOC~\cite{LIU_TMC11_2}, a distributed clustering scheme pursuing cluster robustness.
\item Centralized robust clustering scheme. 
As shown in Section~\ref{centralized_solution}, the centralized robust clustering scheme is formulated as an integer linear optimization problem and is solved by MATLAB with the function $bintprog$.
\end{itemize}

@@

%This means that the sizes of the clusters generated by ROSS-DGA are limited by the network density, and the size control feature further restricts the appearances of the big clusters, thus when the variants of ROSS are implemented, most of the CR nodes are in the clusters which are slightly smaller than the desired size. 
The limitation of distributed scheme ROSS is it doesn't generate clusters whose sizes exceed the cluster head's neighborhood.
The reason is with ROSS, cluster heads form clusters on the basis of their neighborhood, and don't involve the nodes which are outside the neighborhood.

@@

%In the other way around, forming big cluster which extends a cluster head's neighborhood has limited application scenarios, as multiple hop communication and coordination are required within these clusters.
